\tool

### 2018-04-19 paper/paper.tex
Updates to related work section

Although software quality is important, development tools created to improve code quality are often ignored by software engineers~\cite{Ivanov2017Gaps}. Previous work explores barriers preventing software developers from adopting new tools, and researchers have studied challenges to adopting tools for debugging~\cite{CaoDebugging}, static analysis~\cite{Johnson2013Why}, security~\cite{Xiao2014Security}, refactoring~\cite{MurpyHillBarriersRefactoring}, documentation~\cite{ForwardDocumentationRelevance}, and more in their work. One of the main barriers to tool adoption is the discoverability barrier, where users are unaware of a tool's existence~\cite{Murphy-HillScreencastingDiscovery}. This lack of tool awareness in the software engineering industry can lead to the production of poor-quality applications, inconvenienced users, and significant amounts of time and money spent fixing errors. Many existing automated approaches have been implemented to increase awareness of software tools and features, but Murphy-Hill and colleagues found that developers prefer learning about tools from colleagues during normal work activities, or \textit{peer interactions}~\cite{MurphyHill2011PeerInteraction}.

@@

\section{Related Work}
%TODO: Use related work from whatever conference committee
This project builds on previous research examining the intersection between recommendation systems and software engineering.

Previous research has also studied techniques developers use to learn new information. Piorkowski and colleagues applied Information Foraging Theory to software engineers to determined how developers seek information~\cite{FlemingReactiveInformationForaging}. This research differs from these approaches by presenting and implementing a new technique

Prior work has examined help systems for soft in software engineering.

Researchers have created many different approaches for tool recommendations. Fischer and colleagues found that systems requiring users to explicitly seek help, or passive help systems, are ineffective and active help systems are more useful for increasing tool awareness~\cite{Fischer1984ActiveHelpSystems}.

There are several existing automated approaches created to solve the tool discovery problem among software developers.  Gordon and colleagues developed Codepourri, a system using crowdsourcing to make recommendations for Python code~\cite{Gordon2015Codepourri}. Linton and colleagues designed a recommender system called OWL (organization-wide learning) to disseminate tool knowledge using logs throughout a company~\cite{Linton2000OWL}. ToolBox was developed as a ``community sensitive help system'' by Maltzahn to recommend Unix commands~\cite{Maltzahn1995Toolbox}. Answer Garden helps users discover new tools based on common questions asked by colleagues~\cite{Ackerman1990AnswerGarden}. SpyGlass automatically recommends tools to help users navigate code~\cite{Viriyakattiyaporn2010Spyglass}. We developed \tool~to actively suggest useful programming tools and increase awareness for software engineers. Our approach differs from existing recommendation systems in the design and implementation of our tool.

>>>>

Although software quality is important, software engineering tools created to improve code quality are often ignored by developers~\cite{Ivanov2017Gaps}. Previous work explores barriers preventing software engineers from utilizing useful tools for debugging~\cite{CaoDebugging}, static analysis~\cite{Johnson2013Why}, security~\cite{Xiao2014Security}, refactoring~\cite{MurpyHillBarriersRefactoring}, documentation~\cite{ForwardDocumentationRelevance}, and more to help complete programming tasks. Additionally, Tilley and colleagues presented challenges for professional software developers in industry adopting software engineering tools created by researchers, or research-off-the-shelf (ROTS) software~\cite{Tilley2003ROTS}. One barrier to tool adoption is the discoverability barrier, where users are unaware of a tool's existence~\cite{Murphy-HillScreencastingDiscovery}. This lack of tool awareness in the software engineering industry can lead to the production of poor-quality applications, inconvenienced users, and significant amounts of time and money spent fixing errors. Many existing automated approaches have been implemented to increase awareness of software tools and features, but Murphy-Hill and colleagues found that developers prefer learning about tools from colleagues during normal work activities, or \textit{peer interactions}~\cite{MurphyHill2011PeerInteraction}.

@@

\section{Related Work}
%TODO: Use related work from whatever conference committee
This project builds on previous work by researchers examining recommendation systems in software engineering.

Previous research has explored different approaches for recommending tools to software users. Gordon and colleagues developed Codepourri, a system that uses \textit{crowdsourcing} to make recommendations for Python code~\cite{Gordon2015Codepourri}. <gamification> <idea gardening> Linton and colleagues implemented organization-wide learning (OWL) by using system logs make recommendations to employees throughout a company~\cite{Linton2000OWL}. Maltzahn and colleagues developed ToolBox, a ``community sensitive help system'' to recommend Unix commands~\cite{Maltzahn1995Toolbox}. Fischer and colleagues found that systems requiring users to explicitly seek help, or passive help systems, are ineffective and active help systems are more useful for increasing tool awareness~\cite{Fischer1984ActiveHelpSystems}.

Prior work has also studied various techniques to see how software developers learn new information. Piorkowski and colleagues applied \textit{information foraging theory} to software engineers to determined how developers seek information~\cite{FlemingReactiveInformationForaging}. Cockburn and Williams studied pair programming and found it was beneficial for increasing knowledge as a result of 84\% of software engineers they surveyed found it helped them learn `` faster and better
because [they were] always working with a partner''~\cite{Cockburn2001PairProgramming}. <collaborative filtering>, Answer Garden helps users discover new tools based on common questions asked by colleagues~\cite{Ackerman1990AnswerGarden}. Our research presents and implements a novel approach for making tool recommendations to software engineers to increase awareness of useful development tools to help them complete programming tasks.

Toolsmiths have developed automated tools to increase tool discovery among software developers. SpyGlass automatically recommends tools to help users navigate code~\cite{Viriyakattiyaporn2010Spyglass}. We developed \tool~to actively suggest useful programming tools and increase awareness for software engineers. Our approach differs from existing recommendation systems in the design and implementation of our tool.

Existing research has also focused on recommendation styles for tools. <Mike>. This research introduces a novel and distinctive recommendation style based on three unique design principles to increase awareness of useful software engineering tools among developers.
